---
title: "R Notebook for Titanic Dataset"
output: html_notebook
---
```{r}

```

1. Read the train.csv file from the following website:
https://raw.githubusercontent.com/agconti/kaggle-titanic/master/data/train.csv
Have a look at the dataset by using the head, tail, str and summary commands.
```{r}
train.data<- read.csv(file="http://raw.githubusercontent.com/agconti/kaggle-titanic/master/data/train.csv",header=T,sep=",")
train.data
```
#2. Change the Pclass and Survived attributes to factors.
```{r}

```

```{r}
head(train.data)
```
```{r}
tail(train.data)
```
```{r}
str(train.data)
```
```{r}
summary(train.data)
```
```{r}
train.data$Pclass=factor(train.data$Pclass)
train.data$Survived=factor(train.data$Survived)
str(train.data)
```
# 3. Check the missing values of the Age and Name attributes. The Name attribute consists
#of titles such as Miss., Mrs., Mr. and Dr. For a title containing a missing value, assign
#the mean age value for each title not containing a missing value. After these imputations,
#check the missing values of Age.

```{r}
sum(is.na(train.data$Age)== TRUE)
```
```{r}
length(train.data$Age)
```
```{r}
sum(is.na(train.data$Name)==T)
```
```{r}
length(train.data$Name)
```
```{r}
mean.mr = mean(train.data$Age[grepl("Mr\\.",train.data$Name)&!is.na(train.data$Age)])
train.data$Age[grepl("Mr\\.",train.data$Name) & is.na(train.data$Age)]=mean.mr
```
```{r}

```

```{r}
mean.mr = mean(train.data$Age[grepl("Mrs\\.",train.data$Name)&!is.na(train.data$Age)])
train.data$Age[grepl("Mrs\\.",train.data$Name) & is.na(train.data$Age)]=mean.mrs
```


```{r}
mean.mr = mean(train.data$Age[grepl("Dr\\.",train.data$Name)&!is.na(train.data$Age)])
train.data$Age[grepl("Dr\\.",train.data$Name) & is.na(train.data$Age)]=mean.Dr
```

```{r}
mean.miss = mean(train.data$Age[grepl("Miss\\.",train.data$Name)&!is.na(train.data$Age)])
train.data$Age[grepl("Miss\\.",train.data$Name) & is.na(train.data$Age)]=mean.miss
```


```{r}
sum(is.na(train.data$Age))
```
#4. List the distribution of Port of Embarkation. Replace empty entries with NA for Embarked attribute. Assign the two missing values to the most counted port, which is
#Southampton in this case.


```{r}
str(train.data$Embarked)
```
```{r}
table(train.data$Embarked, useNA ="always")
```

```{r}
train.data$Embarked<- replace(train.data$Embarked,train.data$Embarked=="",NA)
```

```{r}
train.data$Embarked[which(is.na(train.data$Embarked))]='S'
table(train.data$Embarked,useNA="always")
```

```{r}
summary(train.data$Embarked)
```
```{r}
summary(train.data$Embarked)
```


